---
framework: lanyon
onefile: False
mode: selfcontained
url: {lib: ../libraries}
---


<!-- 
Updating the bib:
    - must update by hand the file publicationsCVclean.bib in mybib repo
    - once updated, below code downloads current version and loads into R
    - must reference relevant article in relevant pane (publications or presentations)
Afterwards, update the following:
    - Your CV
    - Research Gate
    - Academia EDU
    - Google scholar
-->




<style>
.tempTimes {
    font-family: arial;
    font-size: 0.9em;
    color: #505050;
}
</style>




## Research

```{r, eval=TRUE, echo=FALSE, cache=FALSE}
library(RefManageR)

fileUrl <- "https://raw.githubusercontent.com/jvcasill/mybib/master/publicationsCVclean.bib"
download.file(fileUrl, destfile = "./data/publicationsCVclean.bib", method = "curl")
# list.files("./data")

bib <- ReadBib("./data/publicationsCVclean.bib", check = FALSE)
```



<p></p>
<div class="tabbable">
    <ul class="nav nav-tabs nav-justified" id="myTab">
        <li class="active">
            <a href="#current-research" data-toggle="tab">Current research</a>
        </li>
        <li class="">
            <a href="#publications" data-toggle="tab">Publications</a>
        </li>
        <li class="">
            <a href="#presentations" data-toggle="tab">Presentations</a>
        </li>
    </ul>


    <div class="tab-content">
        <div class="tab-pane active" id="current-research">
            <p>I am an active member of the <a alt="AAPL" href="http://aaplab1.github.io" target='_new'><span class="showtooltip" title="AAPL webpage">Arizona Applied Phonetics Laboratory</span></a> at the University of Arizona. My main interests are in phonetics/phonology. My current projects deal with acquisition of L2 phonology in late learners. Specifically, I am interested in category formation and the production/perception relationship. I am also interested in how dialectal variation affects linguistic attitudes.</p>
        </div>





















        <!-- START TAB 2 -->
        <div class="tab-pane fade" id="publications" style="margin-left:2em;text-indent:-2em">
            <h4>Recent Publications</h4>
            <!-- <div class="minip"> -->

<span class="tempTimes">




```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "CasillasPhonetica2015"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authoryear"))
```

            <!-- START METADATA -->
            <div style="text-indent:.25em;margin-top:-1em" align="left">
            ( <a alt="SDPHON2015" href="" target='_new'><span class="showtooltip" title="Read paper">Link</span></a> |
            <a href="javascript:ReverseDisplay('CasillasPhonetica2015')">Abstract</a> |
            <a href="javascript:ReverseDisplay('CasillasPhonetica2015bib')">Bib </a> )

                <div id="CasillasPhonetica2015" style="display:none;margin-left:2em;text-indent:0em">
                <p class="minip">The present study explored the production and perception of the /i/-/ɪ/ vowel contrast in second language (L2)-dominant early learners of American English who no longer fluently speak their first language (L1, Spanish). The production task analyzed the extent to which the early learner group differed from controls (native English speakers and L1-Spanish late-onset learners of English) with regard to duration and spectral centroids. The perception experiment examined how these early learners classified resynthesized stimuli drawn from the /i/-/ɪ/ con- trast using distinct acoustic cues – spectral and temporal – in a 2-alternative forced choice identification task. The first experiment revealed that the early learners produced the contrast in a native-like manner in terms of the spectral envelope and duration use. The second experiment found that early learners differed from both control groups in how they categorized the /i/-/ɪ/ continua based on spectrum and duration, and the extent to which they rely on these two cues. The effects of linguistic experience on L2 phonetic behavior are discussed.</p>
                </div>

                <div id="CasillasPhonetica2015bib" style="display:none" class="minip">

<pre><code style="margin-top:-1em">
```{r, echo=FALSE}
toBiblatex(bib[key = "CasillasPhonetica2015"], .opts = list(style = "html"))
```
</code></pre>

                </div>
            </div> 
            </br>
            <!-- END METADATA -->










```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "CasillasSimonetSLR2015"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authoryear"))
```

            <!-- START METADATA -->
            <div style="text-indent:.25em;margin-top:-1em" align="left">
            ( <a alt="SDSLR2015" href="http://slr.sagepub.com/content/early/2015/10/09/0267658315608912.abstract" target='_new'><span class="showtooltip" title="Read paper">Link</span></a> |
            <a href="javascript:ReverseDisplay('CasillasSimonetSLR2015')">Abstract</a> |
            <a href="javascript:ReverseDisplay('CasillasSimonetSLR2015bib')">Bib </a> )

                <div id="CasillasSimonetSLR2015" style="display:none;margin-left:2em;text-indent:0em">
                <p class="minip">This study investigates how fluent second-language (L2) learners of English produce and perceive the /æ/–/ɑ/ vowel contrast of Southwestern American English. Two learner groups are examined: (1) early, proficient English speakers who were raised by Spanish-speaking families but who became dominant in English during childhood and, as adults, lack communicative abilities in Spanish, and (2) Spanish-speaking late learners of English who continue to be dominant in Spanish. The participants provided data in three tasks: one production and two perceptual. The study finds that both learner groups differ from native controls in their production and perception of the /æ/–/ɑ/ contrast. The findings shed light on our understanding of the relative effects of age (at onset of language exposure) and language dominance (at time of testing) by showing that sequential bilingualism impacts phonetic behavior even when speakers have become dominant in the target language.</p>
                </div>

                <div id="CasillasSimonetSLR2015bib" style="display:none" class="minip">

<pre><code style="margin-top:-1em">
```{r, echo=FALSE}
toBiblatex(bib[key = "CasillasSimonetSLR2015"], .opts = list(style = "html"))
```
</code></pre>

                </div>
            </div> 
            </br>
            <!-- END METADATA -->





```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "CasillasDiazSimonetICPhS2015article"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authoryear"))
```

            <!-- START METADATA -->
            <div style="text-indent:.25em;margin-top:-1em" align="left">
            ( <a alt="ICPhS2015" href="https://www.researchgate.net/publication/280840068_ACOUSTICS_OF_SPANISH_AND_ENGLISH_CORONAL_STOPS" target='_new'><span class="showtooltip" title="Read paper">Link</span></a> |
            <a href="javascript:ReverseDisplay('CasillasDiazSimonetICPhS2015article')">Abstract</a> |
            <a href="javascript:ReverseDisplay('CasillasDiazSimonetICPhS2015bib')">Bib </a> )

                <div id="CasillasDiazSimonetICPhS2015article" style="display:none;margin-left:2em;text-indent:0em">
                <p class="minip">This study explores the acoustic correlates that distinguish coronal stops (/t/, /d/) between English and Spanish. English and Spanish coronal stops are hypothesized to differ in terms of voice-onset time and place of articulation. We are particularly concerned with capturing the place of articulation difference with acoustic data, as the voice-onset time difference is well known. Specifically, we focus on English /d/ and Spanish /t/, which are phonetically-voiceless stops with a short-lag voice-onset time. Spanish /t/ has been described as being articulated at dental place, whereas English /d/ is articulated at alveolar place. Mixed-effects models explored various spectral measurements of the consonant burst and found that standard deviation, relative burst intensity, and center of gravity differed as a function of place of articulation (or language).</p>
                </div>

                <div id="CasillasDiazSimonetICPhS2015bib" style="display:none" class="minip">

<pre><code style="margin-top:-1em">
```{r, echo=FALSE}
toBiblatex(bib[key = "CasillasDiazSimonetICPhS2015article"], .opts = list(style = "html"))
```
</code></pre>

                </div>
            </div> 
            </br>
            <!-- END METADATA -->



```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "SimonetCasillasDiazSP72014article"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authoryear"))
```

            <!-- START METADATA -->
            <div style="text-indent:.25em;margin-top:-1em" align="left">
            ( <a alt="SpeechProsody" href="https://www.researchgate.net/publication/272090285_The_effects_of_stressaccent_on_VOT_depend_on_language_%28English_Spanish%29_consonant_%28d_t%29_and_linguistic_experience_%28monolinguals_bilinguals%29" target='_new'><span class="showtooltip" title="Read paper">Link</span></a> |
            <a href="javascript:ReverseDisplay('SimonetCasillasDiazSP72014')">Abstract</a> |
            <a href="javascript:ReverseDisplay('SimonetCasillasDiazSP72014bib')">Bib </a> )

                <div id="SimonetCasillasDiazSP72014" style="display:none;margin-left:2em;text-indent:0em">
                <p class="minip">This study examines Voice Onset Times of coronal stops in utterance-initial position in two languages. Crucially, the effects of lexical stress (stressed, unstressed syllable) on VOT are analyzed. The study investigates aspirated stops (English /t/), short-lag voiceless stops (English /d/, Spanish /t/) and pre-voiced stops (Spanish /d/). Three groups of speakers provide data: English monolinguals, Spanish monolinguals, and proficient Spanish-English bilinguals. The study finds that lexical stress lengthens aspiration (English /t/) and prevoicing (Spanish /d/) but it does not alter significantly short-lag stops (Spanish /t/, English /d/). Monolinguals and bilinguals differ slightly in their phonetic behavior. Implications for gestural coordination as well as for feature theory are discussed.</p>
                </div>

                <div id="SimonetCasillasDiazSP72014bib" style="display:none" class="minip">

<pre><code style="margin-top:-1em">
```{r, echo=FALSE}
toBiblatex(bib[key = "SimonetCasillasDiazSP72014article"], .opts = list(style = "html"))
```
</code></pre>

                </div>
            </div> 
            </br>
            <!-- END METADATA -->




```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "CasillasWSS62013article"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authoryear"))
```
            <!-- START METADATA -->
            <div style="text-indent:.25em;margin-top:-1em" align="left">
            ( <a alt="WSS6" href="http://www.lingref.com/cpp/wss/6/abstract2867.html" target='_new'><span class="showtooltip" title="WSS6 abstract">Link</span></a> |
            <a href="javascript:ReverseDisplay('CasillasWSS62013Abstract')">Abstract</a> |
            <a href="javascript:ReverseDisplay('CasillasWSS62013Bib')">Bib </a> )

                <div id="CasillasWSS62013Abstract" style="display:none;margin-left:2em;text-indent:0em">
                <p class="minip">La presente investigación examina las actitudes lingüísticas que tienen los hablantes de español de la comunidad de habla de Tucson, Arizona hacia el dialecto sonorense. Concretamente, se investiga el efecto que tiene la realización del africado prepalatal sordo y su variante fricativa no estándar sobre las percepciones de credibilidad de 4 candidatos a un puesto de trabajo hipotético. Un cuestionario basado en los índices de credibilidad utilizados por McCroskey (1999) se distribuyó a 111 participantes para medir sus actitudes hacia los 4 candidatos. El experimento consistió en una variación de la técnica matched-guise para asignar a los participantes a uno de dos grupos, el primero escuchó la variante estándar y el segundo la variante fricativa. Se demuestra que la variante fricativa recibe valoraciones de credibilidad más bajas que la variante estándar.</p>
                </div>

                <div id="CasillasWSS62013Bib" style="display:none" class="minip">

<pre><code style="margin-top:-1em">
```{r, echo=FALSE, eval=TRUE}
toBiblatex(bib[key = "CasillasWSS62013article"])
```
</code></pre>
                </div>
            </div>
            </br>
            <!-- END METADATA -->



```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "Casillas2012divergencias"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authoryear"))
```

            <!-- START METADATA -->
            <div style="text-indent:.25em;margin-top:-1em" align="left">
            ( <a alt="Divergencias" href="http://divergencias.arizona.edu/sites/divergencias.arizona.edu/files/articles/FricativizacionDivergencias.pdf" target='_new'><span class="showtooltip" title="Read paper">Link</span></a> |
            <a href="javascript:ReverseDisplay('Casillas2012Abstract')">Abstract</a> |
            <a href="javascript:ReverseDisplay('Casillas2012Bib')">Bib </a> )

                <div id="Casillas2012Abstract" style="display:none;margin-left:2em;text-indent:0em">
                <p class="minip">La fricativización del fonema /ʧ/ supone uno de los procesos fonológicos más productivos del español mexicano, sin embargo, actualmente sigue siendo uno de los menos estudiados. Partiendo de las investigaciones de Cedergren (1973), Brown (1989) y Herrera (2006), el presente estudio analiza la fricativización del fonema /ʧ/ en el español de las mujeres del sur de Arizona. El uso de una regresión de subida y bajada de Goldvarb X determinó que la edad de las participantes, el contexto posterior a /ʧ/ y el lugar de nacimiento son factores determinantes para la realización de la variante fricativa.</p>
                </div>

                <div id="Casillas2012Bib" style="display:none" class="minip">

<pre><code style="margin-top:-1em">
```{r, echo=FALSE, eval=TRUE}
toBiblatex(bib[key = "Casillas2012divergencias"])
```
</code></pre>
                </div>
            </div>
            </br>
            <!-- END METADATA -->




```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "Casillas2010gaceta"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authoryear"))
```

            <!-- START METADATA -->
            <div style="text-indent:.25em;margin-top:-1em" align="left">
            ( <a href="javascript:ReverseDisplay('Casillas2010Bib')">Bib</a> )

                <div id="Casillas2010Bib" style="display:none" class="minip">

<pre><code style="margin-top:-1em">
```{r, echo=FALSE, eval=TRUE}
toBiblatex(bib[key = "Casillas2010gaceta"])
```
</code></pre>
                </div>
            </div>
            </br>
            <!-- END METADATA -->



```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "Casillas2009gaceta"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authoryear"))
```

            <!-- START METADATA -->
            <div style="text-indent:.25em;margin-top:-1em" align="left">
            ( <a href="javascript:ReverseDisplay('Casillas2009Abstract')">Abstract</a> |
            <a href="javascript:ReverseDisplay('Casillas2009Bib')">Bib </a> )

                <div id="Casillas2009Abstract" style="display:none;margin-left:2em;text-indent:0em">
                <p class="minip">El refrán es una de las partes fundamentales de la lengua castellana que vemos plasmada en toda la cultura española, tanto en el habla cotidiana como en la literatura. El refrán ha tenido y sigue teniendo suma importancia a la hora de conocer y entender la cultura hispana, ya sea oral o en textos escritos. Es algo que los estudiantes de español como segunda lengua pueden comprobar puesto que supone un reto en su aprendizaje. Como es bien sabido, El Quijote, novela estudiada exhaustivamente desde que fue publicada por primera vez, es una fuente paremiológica imprescindible para quien quiera aprender, investigar o simplemente gozar del refranero cervantino. En palabras de Tarnovska: “No hay otra obra literaria que sea ni pueda ser considerada refranero popular de la misma importancia que El Quijote” (287). Además de ser una de las obras de literatura más esenciales de todos los tiempos, también es un recurso, una vía por medio de la cual el lector puede acercarse a la cultura española.</p>
                </div>

                <div id="Casillas2009Bib" style="display:none" class="minip">

<pre><code style="margin-top:-1em">
```{r, echo=FALSE, eval=TRUE}
toBiblatex(bib[key = "Casillas2009gaceta"])
```
</code></pre>
                </div>
            </div>
            <!-- END METADATA -->












            <h4>Submitted</h4>

```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "LlmopartCasillasJASAEL2016"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authoryear"))
```


            <h4>In preparation</h4>

```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "CasillasDICT2015"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authoryear"))
```

            </span>
            <!-- </div> -->
        </div> <!-- END TAB 2 -->
























        <!-- THIRD TAB BEGIN-->
        <div id="presentations" class="tab-pane fade" style="margin-left:2em;text-indent:-2em">
            <h4>Presentations</h4>

<span class="tempTimes">

```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "CasillasDiazSimonetHLS2015"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
print(bib[key = "BessettCasillasMartinezWSS72014conf"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
print(bib[key = "CasillasSLRF2013"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
print(bib[key = "CasillasPAPI2013"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
print(bib[key = "CasillasWSS6CONF2013conf"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
print(bib[key = "CasillasSYMP2012conf"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
print(bib[key = "CasillasCONF2011symp"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
print(bib[key = "CasillasCONF2011share"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
```


            <h4>Poster presentations</h4>

```{r, results='asis', echo=FALSE, eval=TRUE}
print(bib[key = "CasillasDiazSimonetICPhS2015poster"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
print(bib[key = "SimonetCasillasDiazHLS2014poster"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
print(bib[key = "SimonetCasillasDiazSP72014poster"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
print(bib[key = "CasillasPPLC2013"], .opts = list(check.entries = FALSE, style = "html", bib.style = "authortitle"))
```

        </span>
        </div> <!-- END THIRD TAB -->
    </div> <!-- END TAB CONTENT -->
</div>




<script type="text/javascript" language="JavaScript">
  function HideContent(d) {
  document.getElementById(d).style.display = "none";
  }
  function ShowContent(d) {
  document.getElementById(d).style.display = "block";
  }
  function ReverseDisplay(d) {
  if(document.getElementById(d).style.display == "none") { document.getElementById(d).style.display = "block"; }
  else { document.getElementById(d).style.display = "none"; }
  }
</script>

<script type="text/javascript">  
        $(document).ready(function () {  
            $('.dropdown-toggle').dropdown();  
        });  
</script>
