---
author: "Joseph V. Casillas"
output:
  knitrBootstrap::bootstrap_document:
    title: "cf games"
    theme: united
    highlight: sunburst
    theme.chooser: TRUE
    highlight.chooser: TRUE
---


# Results - overall

```{r, external-code-0, cache=FALSE, results='hide',echo=FALSE}
library(knitr)
source('stats/00_lb_scrape_overall.R')
```

## Overall men
```{r, results='asis'}
knitr::kable(head(data_men_overall, 60), row.names=FALSE)
```

## Overall women

```{r, results='asis'}
knitr::kable(head(data_women_overall, 60), row.names=FALSE)
```

## Average scores

| Workout    | 14.1 | 14.2 | 14.3 | 14.4 | 14.5 |
|:-----------|:-----|:-----|:-----|:-----|:-----|
| Men | `r mean(data_men_overall$'14.1 score')` (`r sd(data_men_overall$'14.1 score')`) | `r mean(data_men_overall$'14.2 score')` (`r sd(data_men_overall$'14.2 score')`) | `r mean(data_men_overall$'14.3 score')` (`r sd(data_men_overall$'14.3 score')`) | `r mean(data_men_overall$'14.4 score')` (`r sd(data_men_overall$'14.4 score')`) | NA |
| Women | `r mean(data_women_overall$'14.1 score')` (`r sd(data_women_overall$'14.1 score')`) | `r mean(data_women_overall$'14.2 score')` (`r sd(data_women_overall$'14.2 score')`) | `r mean(data_women_overall$'14.3 score')` (`r sd(data_women_overall$'14.3 score')`) | `r mean(data_women_overall$'14.4 score')` (`r sd(data_women_overall$'14.4 score')`) | NA |

# Results - by region

```{r, external-code-x, cache=FALSE, results='hide',echo=FALSE}
source('stats/combine_all_regions.R')
```

## Africa

```{r, results='asis'}
knitr::kable(head(data_men_overall_africa, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_africa, 3), row.names=FALSE)
```

## Asia

```{r, results='asis'}
knitr::kable(head(data_men_overall_asia, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_asia, 3), row.names=FALSE)
```

## Australia

```{r, results='asis'}
knitr::kable(head(data_men_overall_australia, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_australia, 3), row.names=FALSE)
```

## Canada East

```{r, results='asis'}
knitr::kable(head(data_men_overall_canadaeast, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_canadaeast, 3), row.names=FALSE)
```

## Canada West

```{r, results='asis'}
knitr::kable(head(data_men_overall_canadawest, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_canadawest, 3), row.names=FALSE)
```

## Central East

```{r, results='asis'}
knitr::kable(head(data_men_overall_centraleast, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_centraleast, 3), row.names=FALSE)
```

## Europe

```{r, results='asis'}
knitr::kable(head(data_men_overall_europe, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_europe, 3), row.names=FALSE)
```

## Latin America

```{r, results='asis'}
knitr::kable(head(data_men_overall_latinamerica, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_latinamerica, 3), row.names=FALSE)
```

## Mid Atlantic

```{r, results='asis'}
knitr::kable(head(data_men_overall_midatlantic, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_midatlantic, 3), row.names=FALSE)
```

## North Central

```{r, results='asis'}
knitr::kable(head(data_men_overall_northcentral, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_northcentral, 3), row.names=FALSE)
```

## North East

```{r, results='asis'}
knitr::kable(head(data_men_overall_northeast, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_northeast, 3), row.names=FALSE)
```

## Northern California

```{r, results='asis'}
knitr::kable(head(data_men_overall_northerncalifornia, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_northerncalifornia, 3), row.names=FALSE)
```

## North West

```{r, results='asis'}
knitr::kable(head(data_men_overall_northwest, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_northwest, 3), row.names=FALSE)
```

## South Central

```{r, results='asis'}
knitr::kable(head(data_men_overall_southcentral, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_southcentral, 3), row.names=FALSE)
```

## South East

```{r, results='asis'}
knitr::kable(head(data_men_overall_southeast, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_southeast, 3), row.names=FALSE)
```

## Southern California

```{r, results='asis'}
knitr::kable(head(data_men_overall_southerncalifornia, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_southerncalifornia, 3), row.names=FALSE)
```

## South West

```{r, results='asis'}
knitr::kable(head(data_men_overall_southwest, 3), row.names=FALSE)
```

```{r, results='asis'}
knitr::kable(head(data_women_overall_southwest, 3), row.names=FALSE)
```

# References

- ref 1

