---
title: "How to create elegant waveform/spectrogram images in R"
description: |
  In this post I show how to generate waveform/spectrogram graphics in R. 
date: "2024-04-18"
author:
  - name: Joseph V. Casillas 
    url: https://www.jvcasillas.com
    affiliation: Rutgers University
    affiliation_url: https://www.rutgers.edu
base_url: https://www.jvcasillas.com
categories: [phonetics, praat, dataviz]
twitter:
  creator: "@jvcasill"
engine: knitr
---

```{r}
#| label: setup
#| include: false

library("praatpicture")
library("here")
```

# The problem

Generating elegant dataviz for spectrogram/waveforms can be cumbersome. 
[Praat](https://www.fon.hum.uva.nl/praat/) has excellent plotting capabilities, but can be rather difficult to teach, especially if you want to plot the waveform/spectrogram/textgrid combination. 
I posted on the topic [a long time ago](https://www.jvcasillas.com/posts/2013-05-09_colored_spectrograms_in_r/2013-05-09_colored_spectrograms_in_r.html) for a solution in R, and this post is an update of sorts, particularly for those not interested in working in Praat directly. 

# The solution

[Rasmus Puggaard-Rode's](https://rpuggaardrode.github.io) fantastic package [praatpicture](https://github.com/rpuggaardrode/praatpicture) makes the process trivial. 
Assume we have a wav file called `welcome.wav` and the corresponding textgrid `welcome.TextGrid`. 
We can plot the wavform/spectrogram/textgrid combination with a simple call to `praatpicture()`:  

```{r}
#| label: fig-welcome-simple
#| fig-asp: 0.56 
#| out-width: "100%"
#| fig-dpi: 300
praatpicture(sound = "welcome.wav")
```

I won't go through all of the capabilities of the package (the documentation is great), but here are a few of my common use cases. 


```{r}
#| label: fig-welcome-formants
#| fig-asp: 0.56 
#| out-width: "100%"
#| fig-dpi: 300
praatpicture(
  sound = "welcome.wav", 
  spec_freqRange = c(0, 4900),
  frames = c('sound', 'spectrogram', 'TextGrid'), 
  formant_plotOnSpec = TRUE, 
  formant_color = '#cc0033'
)
```

```{r}
#| label: fig-welcome-color
#| fig-asp: 0.56 
#| out-width: "100%"
#| fig-dpi: 300
praatpicture(
  sound = "welcome.wav", 
  spec_freqRange = c(0, 4900),
  frames = c('spectrogram'), 
  spec_color = c(
    'darkblue', 'blue', 'cyan', 'yellow', 'orange', 'brown', '#cc0033')
  )
```

```{r}
#| label: fig-welcome-more-color
#| fig-asp: 0.56 
#| out-width: "100%"
#| fig-dpi: 300
praatpicture(
  sound = "welcome.wav", 
  spec_freqRange = c(0, 4900),
  frames = 'spectrogram', 
  spec_color = c("white", scales::pal_brewer(palette = "Reds")(9))
  )
```

```{r}
#| label: fig-welcome-even-more-color
#| fig-asp: 0.56 
#| out-width: "100%"
#| fig-dpi: 300
praatpicture(
  sound = "welcome.wav", 
  spec_freqRange = c(0, 4900),
  frames = 'spectrogram', 
  spec_color = c(viridis::viridis_pal(option = "B")(8), "#cc0033")
  )
```

## Reproducibility information

This document was written in `quarto`.

**Session info**  

```{r}
#| label: session-info
#| echo: false
devtools::session_info()$platform
as.data.frame(devtools::package_info())[, c(3, 8)]
```
